%
% LaTeX report template 
%
\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{subfig}
\usepackage[section]{placeins}
\usepackage{amsmath}
\usepackage{url}
\usepackage{float}
\usepackage{textcomp}
%
\begin{document}

   \title{FYS-STK4155\\ Applied data analysis and machine learning \newline \newline \large Analysis of the 2012 and 2016 US presidential elections}
   \par
   \author{By: Henry Haugsten Hansen \  and \  Fred Marcus John Silverberg}
          
   \date{December 17th 2018}

   \maketitle
\input{abstract_1}
   \newpage
   \tableofcontents
\input{introduction}
\input{theory}
   \newpage
\input{code}
   \newpage
\input{Results.tex}
\input{discussion}
\input{conclusion}
\input{appendix}
\newpage
\begin{thebibliography}{1}
    \bibitem{Data} GeoDa. 2017. 2012 and 2016 Presidential Election. [ONLINE] Available at: https://s3.amazonaws.com/geoda/data/election.zip. [Accessed 13 November 2018].
    \bibitem{Bias and variance} An Introduction to Statistical Learning with Applications in R, (Gareth James, Daniela Witten, Trevor Hastie, Robert Tibshirani). Page 33.
    \bibitem{Standardizing} Hands-On Machine Learning with Scikit-Learn and TensorFlow, (Aurélien Géron). Page 95.
    \bibitem{Faul} A. C. Faul. A concise Introduction to Numerical Analysis. Newton's method. Page 116-119. 
    \bibitem{Morten_log} Morten Hjorth-Jensen. 2018. Data Analysis and Machine  Learning: Logistic Regression. [ONLINE] Available at: https://compphysics.github.io/MachineLearning/doc/pub/LogReg/html/LogReg.html. [Accessed December 2. 2018].    
    \bibitem{Morten} Morten Hjorth-Jensen. 2018. Data Analysis and Machine  Learning: Neural Network. [ONLINE] Available at: https://compphysics.github.io/MachineLearning/doc/pub/NeuralNet/pdf/NeuralNet-minted.pdf. [Accessed December 2. 2018].
    \bibitem{Michael_3} Michael Nielsen. 2018. Neural Networks and Deep Learning. [ONLINE] Available at: http://neuralnetworksanddeeplearning.com/chap3.html.
    \bibitem{RN} Ritchie Ng. 2018. Support Vector Machines [ONLINE] Available at: https://www.ritchieng.com/machine-learning-svms-support-vector-machines/ [Accessed 14 December 2018].
    \bibitem{SK} $Scikit-learn$. 2018. RBF SVM parameters. [ONLINE] Available at: $https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html$ [Accessed 14 December 2018].
   
\end{thebibliography}

Link to Python scripts and latex scripts repository:\\
https://github.com/silverberg89/FYS-STK4155/tree/master/Project3

\end{document}